\documentclass{article}

\title{Standard-Model-Candidate Observables From Finite-Capacity Causal Networks}
\author{Abraham Greenman}
\date{}

\begin{document}
\maketitle

\section{Claim Boundary}

This Paper 8 package records the SMC-001 upstream binding through the closed
Paper 7 conditional particle-excitation observables theorem. It also closes
SMC-002 as a finite candidate sector-family catalog observable row, SMC-003
as finite candidate interaction-family signatures, and SMC-004 as
compatibility with the closed Paper 7 particle-excitation observable rows,
SMC-005 as catalog conservation/coarse-graining stability, SMC-006 as Paper 7
regime consistency and upstream-bypass rejection, SMC-007 as the
no-hidden-observed-catalog/physical Standard Model import audit, and SMC-008
as the final internal conditional Standard-Model-candidate observables
certificate. It closes only the internal conditional Paper 8 theorem. It does
not prove observed particle catalog recovery, physical Standard Model
content, physical particle excitations, physical matter fields, physical
gauge fields, physical quantum dynamics, continuum quantum field theory,
physical nature realization, or a unified field theory.

\section{Closed Catalog Row}

SMC-002 defines finite intrinsic candidate sector-family catalog rows with
finite family labels, finite excitation-label support inherited from Paper 7,
finite charge/gauge signature support inherited from Paper 6, finite local
support and readout boundaries, finite-capacity compatibility,
bounded-transfer compatibility, and compatibility with Paper 7 excitation and
transition rows. SMC-002 does not import observed particle catalogs, physical
Standard Model content, physical particle excitations, continuum QFT,
background Hilbert bundles, simulation-only signals, fit shortcuts, physical
quantum dynamics, or unified-field promotion.

\section{Closed Interaction-Signature Row}

SMC-003 defines finite candidate interaction-family signatures over local
transition neighborhoods with finite interaction-family labels, finite
source/target candidate-family labels, finite source/target excitation
labels, finite charge/gauge delta signatures, finite local transition support
and readout boundaries, finite-capacity compatibility, bounded-transfer
compatibility, and compatibility with Paper 7 excitation and transition rows.
SMC-003 does not import physical scattering theory, Standard Model
Lagrangians, continuum gauge groups, S-matrix structure, external dynamics,
observed particle catalogs, physical Standard Model content, physical
particle excitations, continuum QFT, background Hilbert bundles,
simulation-only signals, fit shortcuts, physical quantum dynamics, or
unified-field promotion.

\section{Closed Paper 7 Compatibility Row}

SMC-004 binds the closed SMC-002 catalog rows and closed SMC-003
interaction-family signatures to the closed Paper 7 finite excitation-sector,
transition/interaction, matter/gauge compatibility, and
conservation/coarse-graining rows. It preserves finite label/support,
charge/gauge signature support, local readout boundaries, finite capacity,
bounded transfer, and causal-cone/no-signaling constraints. SMC-004 does not
import observed particle catalogs, physical Standard Model content, physical
particle excitations, continuum QFT, background Hilbert bundles,
simulation-only signals, fit shortcuts, physical quantum dynamics, or
unified-field promotion.

\section{Closed Conservation And Coarse-Graining Row}

SMC-005 records finite catalog continuity, finite interaction conservation,
bounded catalog flux/transfer, intrinsic coarse-graining maps, non-growing
coarse family, interaction, support, and transfer bounds, and coarse-row
compatibility with SMC-002, SMC-003, SMC-004, and Paper 7
conservation/coarse-graining rows. SMC-005 does not import external
conservation laws, continuum currents, continuum-limit oracles, observed
particle catalogs, physical Standard Model content, physical particle
excitations, continuum QFT, background Hilbert bundles, simulation-only
signals, fit shortcuts, physical quantum dynamics, or unified-field
promotion.

\section{Closed Paper 7 Regime Row}

SMC-006 consumes the recorded Paper 7 final conditional certificate, enforces
the frozen Paper 1 through Paper 7 commit chain and closed upstream theorem
flags, and rejects upstream mutation, Paper 7 bypass, unapproved Paper 7
revisions, and unrecorded upstream revisions. SMC-006 does not import
observed particle catalogs, physical Standard Model content, physical
particle excitations, continuum QFT, background Hilbert bundles,
simulation-only signals, fit shortcuts, physical quantum dynamics, or
unified-field promotion.

\section{Closed No-Hidden-Import Audit}

SMC-007 audits SMC-001 through SMC-006, theorem docs, proof log, state files,
upstream manifest, Lean gate, Rust gate, publication skeleton, Rust-only
runtime/proof-gate policy, and emits a fail-closed audit certificate. SMC-007
does not import observed particle catalogs, physical Standard Model content,
physical particle excitations, continuum QFT, background Hilbert bundles,
simulation-only signals, fit shortcuts, physical quantum dynamics, physical
promotion, or unified-field promotion.

\section{Closed Final Conditional Certificate}

SMC-008 assembles the final internal conditional Standard-Model-candidate
observables certificate from closed SMC-001 through SMC-007. It emits finite
candidate sector-family catalog observables and finite candidate
interaction-family signatures, preserves Paper 7 particle-excitation
compatibility, conservation/coarse-graining stability, finite capacity,
locality, bounded transfer, and causal-cone/no-signaling constraints,
consumes Paper 7 regime consistency and the no-hidden-observed-catalog/
physical Standard Model import audit, and closes only the internal
conditional Paper 8 theorem.

SMC-008 does not import observed particle catalogs, physical Standard Model
content, physical particle excitations, continuum QFT, background Hilbert
bundles, simulation-only signals, fit shortcuts, physical quantum dynamics,
physical nature promotion, or unified-field promotion.

\end{document}
